Exploratory data analysis

### 2022-07-05 slides/data_checking.Rmd
update pkgs for prelim results slides

```{r}
encoding %>% 
  distinct(subj_num, group, category) %>% 
  mutate(category = fct_relevel(category, "arms", "gems", "musi")) %>% 
  ggplot(aes(x = category, fill = group)) +
  geom_bar() +
  theme(legend.position = 0:1, legend.justification = 0:1, legend.background = element_blank())
```

@@

```{r}
encoding %>% 
  group_by(subj_num, j_score) %>% 
  summarize(resp = mean(resp)) %>% 
  ggplot(aes(x = j_score, y = resp)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score",
       y = "P's mean interest (across facts)")
```

@@

Pearson correlation shown: `r this_cor`

```{r}
r_pics %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy WITH confidence (-50 to 50)")
```

@@

Pearson correlation shown: `r this_cor`

```{r}
r_pics %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp_binary)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)")
```

@@

Pearson correlation shown: `r this_cor`

```{r}
r_source %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy WITH confidence (-50 to 50)")
```

@@

Pearson correlation shown: `r this_cor`

```{r}
r_source %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp_binary)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)")
```

>>>>

```{r}
encoding %>% 
  distinct(subj_num, group, category) %>% 
  mutate(category = fct_relevel(category, "arms", "gems", "musi")) %>% 
  ggplot(aes(x = group, fill = category)) +
  geom_bar() +
  geom_text(aes(label = category), stat = "count", vjust = 1.5, colour = "white") +
  theme(legend.position = 0:1, legend.justification = 0:1, legend.background = element_blank())
```

@@

```{r}
encoding %>% 
  group_by(subj_num, j_score) %>% 
  summarize(resp = median(resp)) %>% 
  ggplot(aes(x = j_score, y = resp)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score",
       y = "P's median interest (across facts)")
```

@@

```{r}
r_pics %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = "Mean accuracy WITH confidence (-50 to 50)",
       title = paste("Pearson correlation:", this_cor))
```

@@

```{r}
r_pics %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp_binary)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)",
       title = paste("Pearson correlation:", this_cor))
```

@@

```{r}
r_source %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy WITH confidence (-50 to 50)",
       title = paste("Pearson correlation:", this_cor))
```

@@

```{r}
r_source %>%
  group_by(subj_num, j_score) %>% 
  summarize(acc = mean(resp_binary)) %>% 
  ggplot(aes(x = j_score, y = acc)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)",
       title = paste("Pearson correlation:", this_cor))
```
